\documentclass[10pt,]{article}

\usepackage{xspace}
\usepackage{amsmath,amssymb}
\usepackage{adjustbox}
\usepackage[dvipsnames]{xcolor}
\usepackage{multirow}
\usepackage{datetime}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage[toc,page]{appendix}
\usepackage[normalem]{ulem} % strikethrough

%% Use these lines for letter-sized paper
\usepackage[paper=letterpaper,
%%             nofoot, % Uncomment to put page number above margin
%%             marginparwidth=1in,     % Length of section titles
%%             marginparsep=.05in,       % Space between titles and text
               margin=1in,               % 1 inch margins
            left=0.75in,
            right=0.75in,
%%             includemp
            ]{geometry}

\title{The Endcap Thermal Model}
\date{\today, \currenttime}
\author{Kurt Brendlinger, Yu-Heng Chen, Sergio Diez Cornell, Claire David}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}
\setlength{\parskip}{2mm}

\begin{document}
\thispagestyle{empty}

%% \today, \currenttime

\maketitle

\tableofcontents

\section{Changes since the previous results}

{ \bf
December 12, 2018: The following adjustments were made to results since the version immediately
following ITK Week in November 2017:}
\begin{itemize}
\item The total analog current of the ABC is now set to 70 mA, based on the advice of Paul Keener.
(The ABC digital current is 42.5 mA.)
\item The ASIC-to-hybrid glue was updated to the ``UV cure glue'' described in the TDR. The previous
  glue used was tra-duct-2902.
\item The thermal conductivity of the PCB (powerboard) underneath the FEAST was changed from 0.3 to
3 Wm$^{-1}$K$^{-1}$, based on measurements and advice from Graham Beck. The barrel and endcap FEAST
thermal impedance values calculated from FEA are now more compatible. The result is a reduced FEAST
temperature in the model.
\item The model now includes two AMACs on R3 (powered by two LDOs); previously only one AMAC was used.
\item A 1.9 mA quiescent current is included in the LDOs providing power to the AMACs.
\end{itemize}

{\bf 
December 18, 2018: The following adjustments were made since circulation of the document on December 12, 2017:}
\begin{itemize}
\item The flux estimates have been changed from ``Step 1.9'' to the ``step 2.2 duals layout'' used in
the Pixel TDR. This should be the latest flux estimate.
\item A bug was fixed in which the pessimistic TID bump parameterization safety factor was not applied.
This increases the maximum power estimates slightly, in the worst-case scenario.
\end{itemize}

{ \bf
April 30, 2018: The following changes were made since December 18, 2018:}
% New system architecture: https://edms.cern.ch/ui/file/1807716/1.14/Full_System_Architecture_1.14_EDMS.pdf
\begin{itemize}
\item The FEAST is replaced by the BPOL12V, however the modeling of this converter (temperature
  and current dependence) has not changed. The powering of the AMAC is now handled by the LINPOL12V
  instead of the BPOL12V (FEAST). This reduces the power associated to the FEAST, and thus the
  temperature.
\item The treatment of LV tape losses and BPOL12V voltages has now been made more consistent. Previously,
  tape resistances were modeled with a flat 10~m$\Omega$ resistance and FEAST voltages were set by hand.
  Now, the tape resistance is set to 20~m$\Omega$ (more conservative) and the
  BPOL12V voltages are calculated on-the-fly using the voltage drop of the BPOL12V+tape of
  the previous modules. These should be updated with more realistic values. See Section~\ref{low_voltage}.
\item Modules R3, R4 and R5 have been updated to include two HV filters and two HVMUXes. The descriptions
  of some quantities ($Q_\text{sensor}$ and leakage current) have been clarified in the cases where two sensors
  exist on one module. Details on the implementation can be found in Section~\ref{highvoltage}.
\item New quantities have been added to the endcap model--see Section~\ref{description_of_output}.
\item The Type-I/II/III/IV LV and HV cable losses and the losses from PP2 are now included in the model. New
  estimates of the Cooling power and the Wall Power (descriptions in Section~\ref{description_of_output})
  are included in the documentation. (Previously, the type-1 losses were modeled as adding 5\% additional power,
  and the outer service losses were also modeled as adding 5\% additional power.)
\item The HCC currents have changed to 95~mA digital, 53~mA analog (148~mA total). (Previous values
  were 125~mA digital, 75~mA analog, 200~mA total.) The digital current is assumed to be 100\% bumped, but
  with a maximum TID bump that is 57\% the size of the ABC TID bump.
\item The ABC currents have remained the same (42.5~mA digital, 70~mA analog).
  The 42.5~mA digital current is now assumed to be 69\% bumped (29~mA), 31\% un-bumped (13~mA).
\item The TID parameterization has been switched to the ABC130$^{*}$ parameterization derived by Kyle
  and referred to as the ``Apr2018'' parameterization in the text. For more details see
  Section~\ref{tid_parameterization_details}.
\end{itemize}

\input{Sections/Introduction.tex}
%\clearpage
\input{Sections/Layout.tex}
%\clearpage
\input{Sections/PowerInputs.tex}
\clearpage
\input{Sections/ThermalImpedances.tex}
\clearpage
\input{Sections/HighVoltage.tex}
\input{Sections/TapeAndCabling.tex}
\clearpage
\input{Sections/OtherInputs.tex}
\clearpage
\input{Sections/Results.tex}
\clearpage
\begin{appendices}
\input{Sections/Results_detailed.tex}
\end{appendices}

\end{document}


